Baseline centering problem

### 2018-12-10 paper/tangotd.tex

\paragraph{Learning navigation.} Define a function $V(s,s')$ that
represents the time spent in $s'$ if starting at $s$ and acting optimally
towards $s'$. It is defined by the Bellman equation
\begin{equation}
V(s,s')=\1_{s=s'}+\gamma \max_a \E_{s_1|s,a} V(s_1,s')
\end{equation}
and also satisfies
\begin{equation}
V(s,s')=\1_{s=s'}+\gamma \sum_{s_{t-1}} V(s,s_{t-1})\max_a
\E_{s_t|s_{t-1},a}\1_{s_t=s'}
\end{equation}
although it's not clear to me how to exploit the last expression. But I
think we have to work from both ends if we want to represent
compositionality of actions... (With the first equation, different values
of $s'$ are just completely separate Bellman problems; the generalization
abilities of the function approximator for $V$ may help, but only so
much.)

@@

>>>>

\paragraph{Learning to navigate.} Define a function $V(s,s')$ that
represents the time spent in $s'$ if starting at $s$ and acting optimally
towards $s'$. It is defined by the Bellman equation
\begin{equation}
V(s,s')=\1_{s=s'}+\gamma \max_a \E_{s_1|s,a} V(s_1,s')
\end{equation}
and also satisfies
\begin{equation}
V(s,s')=\1_{s=s'}+\gamma \sum_{s_{t-1}} V(s,s_{t-1})\max_a
\E_{s_t|s_{t-1},a}\1_{s_t=s'}
\end{equation}
although it's not clear to me how to exploit the last expression. But I
think we have to work from both ends if we want to represent
compositionality of actions... (With the first equation, different values
of $s'$ are just completely separate Bellman problems; the generalization
abilities of the function approximator for $V$ may help, but only so
much.)

@@

Another possibility is to learn a goal-oriented policy towards desired
\emph{features} of the final state $s'$. Given a basis $(\Psi_i)$ of
features, and a set of coefficient $\alpha_i$, one might want
$\pi_\theta(a|s,(\alpha_i))$ to produce a policy that maximizes the
expected reward $\sum \alpha_i \Psi_i$ (thus, simultaneously learning to
solve a number of RL problems). Then we can learn an approximate
decomposition of the actual reward over the $\Psi_i$, and we know what to
do. (This assumes the reward is well approximated by the $\Psi_i$; or
that we learn the complement.) There are many ways to build interesting
$\Psi_i$'s: hidden features of a world model/reward model, eigenfunctions
of $P$, or just setting a basis of random time-dependent functions on a
trajectory and smoothing them via a NN (``zeitgeist'').
